Model_CFU

### 2016-12-07 Projects/HumanCdGF_cdiff_colonization.Rmd
correlation plots for otus correlated to cfu

OTUs predictive of _Colonization level_:  
`r names(top_features)`

@@

set.seed(seed)
source_all_rf <- randomForest(source_all_shared_df[ , -1], source_all_shared_df$human_source,
                           ntree = 501,
                           mtry = 15,
                           importance = T)
top_features_src <- head(sort(importance(source_all_rf)[,1],decreasing = T), n_features)
#any(top_features %in% top_features_src)
src_feat_cor_cfu <- sort(abs(cor(cfu_all_shared_df[ , c('log_cfu_med', 
                                                        names(top_features_src))], 
                                 method = 'spearman')[,'log_cfu_med']), 
                         decreasing = T)
```

OTUs predictive of _Inocula Source_:  
`r names(top_features_src)`

>>>>

#### Predictive OTUs  
##### OTUs predictive of _Colonization level_:  
`r names(top_features)`

@@

set.seed(seed)
source_all_rf <- randomForest(source_all_shared_df[ , -1], source_all_shared_df$human_source,
                           ntree = 501,
                           mtry = 15,
                           importance = T)
top_features_src <- head(sort(importance(source_all_rf)[,1],decreasing = T), n_features)
#any(names(top_features) %in% names(top_features_src))
src_feat_cor_cfu <- sort(abs(cor(cfu_all_shared_df[ , c('log_cfu_med', 
                                                        names(top_features_src))], 
                                 method = 'spearman')[,'log_cfu_med']), 
                         decreasing = T)
```

##### OTUs predictive of _Inocula Source_:  
`r names(top_features_src)`

There are `r sum(names(top_features) %in% names(top_features_src))` OTUs that overlap between predicting Colonization and Source:  
`r names(top_features)[names(top_features) %in% names(top_features_src)]`

#### Predictive OTUs that correlate with CFU  
The following predictive OTUs correlate with CFU (Spearman's _rho_ > 0.5)

Colonization Level  
`r names(feat_cor_cfu)[feat_cor_cfu>0.5 & feat_cor_cfu < 1]`

```{r plot colonization otu correlations, fig.width=10, fig.height=18}
subset(cfu_all_shared_df, select = 
       c("log_cfu_med", names(feat_cor_cfu)[feat_cor_cfu>0.5 & feat_cor_cfu < 1])) %>% 
  gather(OTU, abundance, contains('Otu')) %>% 
  ggplot(aes(x = abundance, y = log_cfu_med)) + geom_point() + 
    facet_wrap(~OTU, ncol = 4, scales = 'free_x')
```

Inocula Source  
`r names(src_feat_cor_cfu)[src_feat_cor_cfu>0.5 & src_feat_cor_cfu < 1]`

```{r plot source otu correlations, fig.width=7.5, fig.height=3}
subset(cfu_all_shared_df, select = 
       c("log_cfu_med", names(src_feat_cor_cfu)[src_feat_cor_cfu>0.5 & src_feat_cor_cfu < 1])) %>% 
  gather(OTU, abundance, contains('Otu')) %>% 
  ggplot(aes(x = abundance, y = log_cfu_med)) + geom_point() + 
    facet_wrap(~OTU, ncol = 3, scales = 'free_x')
```
